---
title: "Assessment 3 - Programming for Sports Performance"
author: "Julian Asta"
date: "2022-08-18"
output: 
  html_document:
    code_folding: hide
---
```{r Programs}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
library(datasets)
library(plotly)
library(heatmaply)

```
# Summary

This is an analysis of the Super Netball season, it will focus on players output in three categories: Defensive, Play making and Offensive. I will also be highlighting players who have stood out in these categories. 


```{r Summary Data}


Data <- read.csv("Data/Dataset3_Assessment3.csv")
view(Data)

summary(Data)

tibble(Data)
```

# Tidying of data

This table shows the data which has been tidyed and condensed to allow for a cleaner look at the certain outputs of players.



```{r Tidying Data}
DataWide <- Data %>%
  pivot_wider(names_from = Statistic, 
              values_from = Total,
              values_fill = 0,
              names_sep = "-")


Data_Clean <- DataWide %>%
  mutate("Defensive Output" = deflectionWithGain+deflectionWithNoGain+intercepts/minutesPlayed) %>%
  mutate("Playmaking Output" = possessions+goalAssists+feeds+feedWithAttempt/minutesPlayed)%>%
  mutate("Offensive Output" = goals+goalAttempts/minutesPlayed)

Data_Clean %>%
  pivot_longer(`Defensive Output`:`Offensive Output`,
               names_to = "Output",
               values_to = "Value")


Data_Clean %>%
  filter(Team == "Melbourne Vixens") %>%
  summarise()
  kbl(Data_Clean) %>%
  kable_styling(full_width = F, html_font = "Cambria")


```

# Defensive Output

This defensive Ouput shows the teams that were successful in creating turnover oppertunities, with GIANTS having the best overall output.

```{r Def Output}
Data_Clean %>%
  ggplot(Data_Clean, mapping = aes(x = Team, y = `Defensive Output`)) +
  geom_boxplot(colour = "blue",
               fill = "blue",
               alpha=0.2,
               notch = FALSE,
               notchwidth = 0.8,
               outlier.colour = "red",
               outlier.fill = "red",
               outlier.size = 3)
```

# Offensive Output

Offensive Output of teams who were more likely to score due to teh oppertunities given, West Coast Fever were successful in being the most efficent in point scoring through both zones.

```{r Off. Output}
Data_Clean %>%
  arrange(Data_Clean == "Offensive Output")
  ggplot(Data_Clean, mapping = aes(fill = Team, x = Team, y = `Offensive Output`))+
  geom_bar(position = "dodge", stat = "identity")
```


```{r Pmk Output}

Data_Clean %>%
  ggplot(Data_Clean, mapping = aes(x = `Playmaking Output`, y = Team))+
  geom_point()

```


# Playmaking Output

This output is closely tied to the offensive output as the teams who were able to score more, were able to do so due to the ability to create efficent passing options to score from.


