---
title: Assessment 3
Output: GitHub Document
---
```{r Programs}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(viridis)
library(kableExtra)
library(datasets)
library(plotly)
library(heatmaply)

```
# Summary

This is an analysis of the Super Netball season, it will focus on players output in three categories: Defensive, Play making and Offensive. I will also be highlighting players who have stood out in these categories. 


```{r Summary Data}


Data <- read.csv("Data/Dataset3_Assessment3.csv")
view(Data)

summary(Data)

tibble(Data)
```

# Tidying of data

This table shows the data which has been tidyed and condensed to allow for a cleaner look at the certain outputs of players.



```{r Tidying Data}
DataWide <- Data %>%
  pivot_wider(names_from = Statistic, 
              values_from = Total,
              values_fill = 0,
              names_sep = "-")


Data_Clean <- DataWide %>%
  mutate("Defensive Output" = deflectionWithGain+deflectionWithNoGain+intercepts/minutesPlayed) %>%
  mutate("Playmaking Output" = possessions+goalAssists+feeds+feedWithAttempt/minutesPlayed)%>%
  mutate("Offensive Output" = goals+goalAttempts/minutesPlayed)

Data_Clean %>%
  pivot_longer(`Defensive Output`:`Offensive Output`,
               names_to = "Output",
               values_to = "Value")


Data_Clean %>%
  filter(Team == "Melbourne Vixens") %>%
  summarise()
  kbl(Data_Clean) %>%
  kable_styling(full_width = F, html_font = "Cambria")


```

# Defensive Output



```{r Def Output}
Data_Clean %>%
  ggplot(Data_Clean, mapping = aes(x = Team, y = `Defensive Output`)) +
  geom_boxplot(colour = "blue",
               fill = "blue",
               alpha=0.2,
               notch = FALSE,
               notchwidth = 0.8,
               outlier.colour = "red",
               outlier.fill = "red",
               outlier.size = 3)
```

# Offensive Output


```{r Off. Output}
Data_Clean %>%
  arrange(Data_Clean == "Offensive Output")
  ggplot(Data_Clean, mapping = aes(fill = Team, x = Team, y = `Offensive Output`))+
  geom_bar(position = "dodge", stat = "identity")
```


```{r Pmk Output}

Data_Clean %>%
  ggplot(Data_Clean, mapping = aes(x = `Playmaking Output`, y = Team))+
  geom_point()

```